\section{Introduction}
Today's cryptography for modern communication systems are mostly based on asymmetric cryptography algorithm, known as public-key cryptography.\\ One of the widely used public-key cryptography algorithm is RSA\footnote{Rivest-Shamir-Adleman : link?}. It is designed around computational hardness assumption which, in the early 2000s was still provable. However with the introduction of the quantum computers these mathematical hardness has been shown vulnerable as quantum computer are known to be able to break system based on integer factorisation.\\
Thus a new mathematical model should be found that could be proved quantum resistant. \\
The NTRU crypto-system is such an alternative based on the closest lattice vector problem (described in background section).\\
Asymmetric cryptography is also a important part of the concept of Internet of Things (IoT). \\In fact the challenge for such hardware is the possibility for secure communication while keeping the hardware cost very low. Symmetric cryptography is already widely used and proven to be performant and cost efficient for such small controller and limited hardware. But symmetric cryptography do provide a low security scheme. \\
The NTRU public-key crypto-system main characteristics are the low memory and computational requirements while keeping a high security level in communication thanks to the asymmetric scheme of encryption. This makes the NTRU crypto-system the perfect candidates for being implemented on IoT hardware ($e.g.$ 8 bit AVR controller).\\
\\
In this work we will go trough the different steps of implementation and performance measurement of  the NTRUencrypt algorithm on an 8 bit AVR controller. Specially for the mask generating utility function used to provide of a variable length primitive output. And if such implementation can approximate the performance of a standard 64 bit computer. 